---
title: Replication of Study 4 by Semrow, Zou, Liu, & Cheryan (2019, Social Psychological
  and Personality Science)
author: "Adrian Apaza (apaza@stanford.edu)"
date: "December 4, 2019"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
---
<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->
[Original paper](https://github.com/psych251/Semrow2019/blob/master/original_paper/semrow2019.pdf) 

[Github repository](https://github.com/psych251/Semrow2019)

[Paradigm](https://stanforduniversity.qualtrics.com/jfe/form/SV_d5OpcZTSNZl1dE9)


##Introduction


This paper by Semrow et al. (2019) studies how membership in different identity categories interact. In this case the researchers find that Asian Americans who are gay are perceived as more American than straight Asian Americans. My primary research is on categories and membership of organizations and individuals with regards to various identity groups and the status attained by membership in different groups. This work interests me In that it displays how membership in one identity group (LGBTQ) influences membership in another group (American), and is useful to my field in that membership in either group affects individual's status and labor market outcomes.  This particular study's materials do not explicitly state that the targets are Asian or Asian American. Other studies within the original paper examined Asian identity explicitly, this one examines foreign identity more broadly and thus this study may have more broad implications than others within the paper. 

The key result of interest in this paper was the following interaction effect. Target individuals who were gay and whose country of origin was less accepting of gay people than the U.S. were seen as more American (relative to the condition where the country of origin was equally accepting) than straight targets whose country of origin was less accepting relative (again relative to the condition where the country of origin was equally accepting).

> A 2 (sexual orientation: gay, straight; between) by􏰃 2 (country of origin: equally accepting, less accepting; within) mixed-model ANOVA on American identity revealed... a significant interaction [between target's sexuality and country acceptance], F(1, 98) = 22.39, p < .001 (page 6).

I attempt to replicate this finding, but I must note that my replication differs from the original regarding its participants. I have recruited Amazon Mechanical Turkers instead of university students.



\begin{comment}
[No abstract is needed.]  Each replication project will have a straightforward, no frills report of the study and results.  These reports will be publicly available as supplementary material for the aggregate report(s) of the project as a whole.  Also, to maximize project integrity, the intro and methods will be written and critiqued in advance of data collection.  Introductions can be just 1-2 paragraphs clarifying the main idea of the original study, the target finding for replication, and any other essential information.  It will NOT have a literature review -- that is in the original publication. You can write both the introduction and the methods in past tense.  
\end{comment}

##Methods

###Power Analysis
\begin{comment}
So from the original paper we the estimated effect size between the two groups of interest (varying sexuality of target) was .79, standard deviations were within each group 1.08 (less accepting country) and .45.
Utilizing t-tests for equality and $\alpha=0.05$ at a power level of .8 we would need 19 in each group, at .9 power we would need 25 per group, and at .95 power we would need 30 per group.

However I would recommend even larger sample sizes since our population being sampled from (M-Turkers) differs from the population selected from in the original study (undergraduate students), since it may be possible that our sample will have greater variance in responses.

\end{comment}

The planned test is an F test for the interaction between target sexuality and country acceptance. I determined that 50 participants ought to be recruited. However I will note that the corresponding author of the original paper mentioned that my proposed sample size may be under powered. I justified my proposed sample with the following analysis. Again this is to replicate the interaction effect:

> A 2 (sexual orientation: gay, straight; between) by􏰃 2 (country of origin: equally accepting, less accepting; within) mixed-model ANOVA on American identity revealed... a significant interaction [between target's sexuality and country acceptance], F(1, 98) = 22.39, p < .001 (page 6).

The parameters of interest are described as follows. I chose $\alpha =0.05$ and power of .95. The estimated results for less and equally accepting countries for a gay target are 4.82 and 4.03 respectively, whereas for a straight target the measures are 3.89 and 4.09 respectively. These estimates are for the measures of perceived Americanness - measured as the mean of three Likert style questions described below in more detail. Regarding the parameters for variance of measures and correlation across measures, I presumed that my participants would have greater variation and so I conducted analysis presuming the variance of the result for a measure is one and the correlation across measures is 0.55 (the correlation of within subject responses to the two conditions).


\begin{comment}
These estimates are based upon the actual study. However given that Mechanical Turkers should vary more than undergrads, I updated the estimated variance such that the standard deviation of results for a measure are expected to be 1.

Based upon these parameters and with $\alpha =0.05$ and for a power of .95, 50 participants ought to be recruited. Had I not had a prior of higher variance then the sample size required would have been lower.

Upon contact with the original study's corresponding author, a higher planned sample was advised due to concerns regarding this proposed replication being under powered.
\end{comment}

###Planned Sample


This is a 2 by 2 study. A total sample of 52 is the planned size (26 per condition). Slightly more than 50 should be recruited in case some fail to complete the survey. Each participant will be presented with either a straight target or a gay target and will receive two conditions regarding the level of acceptance in the country of origin. So within participants the country of origin acceptance is varying and between participants the target's sexuality varies.

The desired sample will consist of Americans using Amazon's Mechanical Turk platform. Although the original study participants were University of Washington students.

###Materials

The materials as follows will be followed as precisely as possible. [Here are the Orignal Materials](https://osf.io/u7wdz/).




> "Participants [will be] presented with a hypothetical country either named Boden or Thamen. They were told either that gay people are less welcome and accepted in Boden/Thamen than in the United States, or that they are equally welcome and accepted in Boden/Thamen and the United States. Then, they read about a gay man (“X is a gay man”) or straight man (“X is a straight man”). Participants rated the target’s American identity on three questions: “How likely is it that this person is Bodenian/Thamenian or American?,” “How Bodenian/Thamenian or American is this person?,” and “To what extent do you believe this person identifies as Bodenian/Thamenian or American?” on a scale from 1 (very [likely] Bodenian/Thamenian) to 7 (very [likely] American)...[Then] They read about another target with the same sexual orientation (“Y is a gay/straight man”) [but changed country and homophobia condition] and answered the same three questions about his American identity" (pages 5-6).

This will be conducted using a Qualtrics survey with MTurk participants. On one page of the survey participants will be presented with relevant information regarding the hypothetical country and the target individual, then on the next page of the survey this information is repeated and the three Likert scale questions are presented. Then on the following page participants will be presented with manipulation checks asking them to identify the acceptance of the country-of-origin relative to the US("How accepting is [Target Country] of gay people compared to the U.S.") on a scale of from 1 (Much less accepting) to 7 (Much More accepting); and the target's sexuality with a multiple choice question: "What was the sexual orientation of the person you read about?" (with responses of Gay, Straight, or Not Specified.



###Procedure/Stimuli and Challenges	

Results may be confounded by the order of the country of origin conditions. Additionally participants may quickly learn about the purpose of the experiment upon being exposed to the second condition. Country names may also confound. Further confounds may also be introduced by the name of the target person. So I have taken care to randomize and fully counterbalance the presentation of the country of origin acceptance conditions, country names and target names. 

Furthermore participants on Mturk may not be paying sufficient attention and fail manipulation checks. However in the original study many participants failed at least one manipulation check, this was because participants incorrectly reported the straight target's sexuality as being "not specified".

###Analysis Plan

I plan to conduct to conduct a 2 by 2 ANOVA as follows to yield an estimate of the study's main result:

> A 2 (sexual orientation: gay, straight; between) by􏰃 2 (country of origin: equally accepting, less accepting; within) mixed-model ANOVA on American identity revealed... a significant interaction [between target's sexuality and country acceptance], F(1, 98) = 22.39, p < .001 (page 6).

Note that the dependent variable is the mean response on the 1-7 question scale for each of the three questions. I hope to replicate the findings such that a significant p-value is yielded from the F test specified above. 

I will analyze the results excluding those results for participants who fail a corresponding manipulation check. A manipulation check is regarded as a failure if the equally accepting country of origin is regarded as less accepting to the U.S. or the less accepting country of origin is regarded as equally or more accepting than the U.S. Additionally failure will occur if the target's sexuality is incorrectly recalled.


I also plan to conduct additional analysis of the demographics of the participants I recruited. I will not examine how responses differ by key demographics, rather I am interested in noticing if the replication study's demographics differ significantly in some respects (e.g. gender identity, race, etc.) from the original study's demographics.

###Differences from Original Study

The primary difference from the original study is the sample. This sample will consist of American mechanical turkers rather than students at a major American research university. This may make a notable difference as undergraduate students at the University of Washington should be expected to have different views of other countries, ethnicity, and sexuality than the broader American population. Additionally my sample will be smaller. Only very slight variations have been made to the materials to account for the fact that this survey is being conducted online rather than physically with paper. These slight changes to the materials have been made in consultation with the original study's corresponding author.

\begin{comment}
### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.
\end{comment}
#### Actual Sample
  <Sample size, demographics, data exclusions based on rules spelled out in analysis pla.n>

#### Differences from pre-data collection methods plan
  <Any differences from what was described as the original plan, or “none”.>


##Results


### Data preparation
For data preparation it is first of all key to exclude participants who fail the manipulation checks as specified earlier. I will note that the only data preparation done before hand was changing the name of the variables for the results to "Condition_1_Results, Manipulation_1_Check", etc. in Excel as they were not named properly upon importing the data in R otherwise.

The data analyzed below is from four participants recruited from a pilot.
```{r include=T,eval=T}

####Load Relevant Libraries and Functions
library(tidyverse)
library(ggplot2)
df<-read.csv('PilotBDataFixedRestricted.csv')
#drop first two rows of irrelevant duplicated information.
df<-df[-c(1,2),]


##Keep relevant information for tests, demographics the manipulations, the measurements, and the manipulation checks
dfRelevant<-(df %>%
  select(Country1Homophobia, Sexuality,Condition_1_Results,Condition_2_Results, Manipulation_1_Check, Manipulation_2_Check,Sexuality_Check_1,Sexuality_Check_2, Gender, Race) )

##Transform into long format
data_long <- gather(dfRelevant, condition, Americanness, Condition_1_Results:Condition_2_Results, factor_key=TRUE)

#Now we only kept the first conditions homophobia since then  we know that the second is opposite.
#So create a variable that corresponds to condition's value for homophobia. In this long format, right now the condition variable is coded as "Condition_1_Results" or "Condition_2_Results"
data_long$condition<-as.character(data_long$condition)
#code such that the less accepting or homophobic country of origin condition is one and 0 otherwise
data_long$CountryAcceptance<-0
##The current condition's country is less accepting if we are on the first condition and it is homophobic or the second condition and the first country is not homophobic (since it varies within participant)
data_long$CountryAcceptance[(data_long$condition=='Condition_1_Results' & data_long$Country1Homophobia==T) | (data_long$condition=='Condition_2_Results' & data_long$Country1Homophobia==F)]<-1


##Collapse the Country and Sexuality Checks into one relevant variable to match the condition.
data_long$CountryManipulationCheck<-as.numeric(as.character(data_long$Manipulation_1_Check))
data_long$CountryManipulationCheck[data_long$condition=='Condition_2_Results']<-as.numeric(as.character(data_long$Manipulation_2_Check[data_long$condition=='Condition_2_Results']))


data_long$SexualityCheck<-data_long$Sexuality_Check_1
data_long$SexualityCheck[data_long$condition=='Condition_2_Results']<-data_long$Sexuality_Check_2[data_long$condition=='Condition_2_Results']

##Now keep only our relevant variables: The dependent variable (Americanness), Sexuality, CountryAcceptance, CountryManipulationCheck, SexualityCheck and demographics
data_long<-(data_long %>%
  select(Americanness, Sexuality,CountryAcceptance,CountryManipulationCheck, SexualityCheck,Gender, Race) )

#Now create variable if particpant  passed checks for country of origin acceptance condition, initalize to 0
data_long$PassedCountryCheck<-0

#now for equally accpeting countries you should answer 4 or above, recall CountryAcceptance value of 0 corresponds to equally acceptin and one as less
data_long$PassedCountryCheck[as.numeric( as.character( data_long$CountryManipulationCheck)) * (1-data_long$CountryAcceptance) >=4 & data_long$CountryAcceptance == 0] <- 1

#For less accepting countries the answer should be less than 4
data_long$PassedCountryCheck[as.numeric( as.character( data_long$CountryManipulationCheck))  < 4 & data_long$CountryAcceptance == 1] <- 1


##Code the sexuality checks as passing if the response equals the target's sexuality
#Initialize to zero
data_long$SexualityCheckPassed<-0
data_long$SexualityCheckPassed[data_long$Sexuality == data_long$Sexuality]<-1



##now we can code if  both checks were passed by multiplying together since both ought to be one
data_long$PassedAllChecks<-0
data_long$PassedAllChecks<-data_long$PassedCountryCheck*data_long$SexualityCheckPassed




###Some Final House-keeping
##Divide Americanness by 3 in order to get the average as the variable was originally summed
data_long$Americanness<-as.numeric(data_long$Americanness)/3


#create new dataframe of those who pased checks to analyze them
data_long_passed<-data_long[data_long$PassedAllChecks==1,]




```

### Confirmatory analysis
```{r include=T,eval=T}
#now conduct the main analysis of the F test for those who passed manipulation check
AnovaAnalysis<-aov(Americanness~Sexuality*CountryAcceptance,data=data_long_passed)
##Get the summary displaying F stats
summary(AnovaAnalysis)
##Get the Coefficients
AnovaAnalysis$coefficients



##now plot the Results

#First convert Country Acceptance Variable to a factor
data_long_passed$Sexuality<-as.factor(data_long_passed$Sexuality)
data_long_passed$CountryAcceptance<-as.factor(data_long_passed$CountryAcceptance)

#Now plot
ggplot(data_long_passed, aes(Sexuality, Americanness, fill = CountryAcceptance)) +
  stat_summary(geom = "bar", fun.y = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  xlab('Target Sexuality') + ylab('Perceived American Identity (1-7 Scale)')+
  scale_fill_discrete(name = "Accepting vs U.S.", labels = c("Equally", "Less"))


```

###Exploratory analyses

Further Analysis will be done to compare the demographic makeup of m-turkers as compared to the original study.

```{r include=T,eval=T}
#Get the proportions of White and Asian / Asian Americans in the data
mean(df$Race=='White')
mean(df$Race=='Asian / Asian American')
#Get the Proportions of male and female identifiers
mean(df$Gender=='Man')
mean(df$Gender=='Woman')


```

## Discussion

<Insert Discussion of my results and estimates compared to theirs>

<Insert discussion of demographic differences - I presume racial demographics will vary significantly >
### Summary of Replication Attempt
\begin{comment}

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  
\end{comment}

### Commentary
\begin{comment}

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
\end{comment}
